Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling

### 2021-01-25 papers/intro_paper/results_synthetic.tex
updated results_synthetic section

\subsection{\ab{Simulations using GR signals in Gaussian noise}} \label{ssec:gr_signal}

\ab{We demonstrate our method using synthetic-signal injections describing GWs
from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and
Virgo detectors at design sensitivities~\cite{}. \comment{AB: Please cite which PSD you used.}
For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{} and
GW190521~\cite{}. We list them in Table~\ref{tab:injection_values}.
These two binary systems are representative of the kind of systems for which
the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the
pre- and post-merger SNRs return reliable parameter-estimation results.}

>>>>

\subsection{Simulations using GR signals in Gaussian noise} \label{ssec:gr_signal}

We demonstrate our method using synthetic-signal injections describing GWs
from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and
Virgo detectors at design sensitivities~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{Abbott:2016blz} and
GW190521~\cite{Abbott:2020tfl}. We list them in Table~\ref{tab:injection_values}.
These two binary systems are representative of the kind of systems for which
the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the
pre- and post-merger SNRs return reliable parameter-estimation results.
